Model Search in Relational Domains

### 2016-10-19 algorithm.tex
algorithm description

For example, a decision in interval domain restrict the range of 
intervals for variables, so the analysis jumps under a 
greatest fixed-point. Note that the widening operation in abstract interpretation 
jumps above a least fixed-point, so decisions can be viewed as 
{\em dual widening}.  The procedure $deduce$ is called next to infer new 
set of meet irreducibles for the current decision.  The model search phase 
alternates between the decision and deduction until the result of deduction 
is either $\gamma$-complete~\cite{gamma} or the deduction leads to a {\em CONFLICT}.  
If $v$ is $\gamma$-complete, then it cannot be refined further.  Thus, the 
algorithm returns the error trace $v$ and terminates with UNSAFE or the 
current abstraction is insufficient to determine the satisfiability of $\varphi$.  
However, in case of {\em CONFLICT}, the algorithm enters in to 
$conflict\_analysis()$ phase to learn the reason for {\em conflict}.  
There can be multiple incomparable reasons for conflict -- based on 
the choice of Unique Implication Point (UIP)~\cite{cdcl}.  ACDCL heuristically 
choose one reason.  A learnt clause must include asserting cuts which 
guarantees derivation of new meet irreducibles after backtracking. The clause 
learning and backtracking continues as long as the result of deduction 
is conflicting ($\perp$), that is, the abstract valuation $v$ does not
abstractly satisfy the formula.  If no further backtrack is possible, 
then the algorithm terminates and $\varphi$ is {\em SAFE}. Else, the 
algorithm makes a new decision and the above process is repeated 
until a real counterexample is obtained or the algorithm backtracks to 
decision level 0 after a conflict in which case it returns {\em SAFE}.

>>>>

For example, a decision in interval domain restrict the range of 
intervals for variables, so the analysis jumps under a 
greatest fixed-point. Note that the widening operation in abstract interpretation 
jumps above a least fixed-point, so decisions can be viewed as 
{\em dual widening}.  The procedure $deduce$ is called next to infer new 
set of meet irreducibles for the current decision.  The model search phase 
alternates between the decision and deduction until the abstract value $v$ 
precisely represents the set of models or the deduction leads to a {\em CONFLICT}.  
Checking whether $v$ precisely represents set of models corresponds to 
$\gamma$-completeness~\cite{dhk2013-popl} check in abstract interpretation.  
If $v$ is $\gamma$-complete, then it cannot be refined further.  Thus, the 
algorithm returns the error trace $v$ and terminates with UNSAFE or the 
current abstraction is insufficient to determine the satisfiability of $\varphi$.  
However, in case of {\em CONFLICT}, the algorithm enters in to 
$conflict\_analysis()$ phase to learn the reason for {\em conflict}.  
There can be multiple incomparable reasons for conflict -- based on 
the choice of Unique Implication Point (UIP)~\cite{cdcl}.  ACDCL heuristically 
choose one reason.  A learnt clause must include asserting cuts which 
guarantees derivation of new meet irreducibles after backtracking. The clause 
learning and backtracking continues as long as the result of deduction 
is conflicting ($\perp$), that is, the abstract valuation $v$ does not
abstractly satisfy the formula.  If no further backtrack is possible, 
then the algorithm terminates and $\varphi$ is {\em SAFE}. Else, the 
algorithm makes a new decision and the above process is repeated 
until a real counterexample is obtained or the algorithm backtracks to 
decision level 0 after a conflict in which case it returns {\em SAFE}.
